Capstone Movielens Report

### 2025-12-23 reports/capstone-movielens.site/05.appendix.Rmd
Report refactoring: references to `Appendix A`.

::: {.noteblock data-latex=""}
In the sample code snippet above, the `mean_reg` function is called internally from the [train_user_movie_effect](#func.train_user_movie_effect) function described below in section *Models Training: Support Functions /* [UME Model: Utility Functions] of *this Appendix*.
:::
:::

@@

::: {.noteblock data-latex=""}
*Regularization* is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Model Tuning Utils] section of *this Appendix*.
:::
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above this function is passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument to the [tune.model_param](#func.tune.model_param) function described above in the section *Common Helper Functions /* [Model Tuning Utils] of *this Appendix*.

@@

::: {.noteblock data-latex=""}
This function is an auxiliary function specifically designed to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Model Tuning Utils] section of *this Appendix*.
:::
:::

@@

::: { #func.train_user_movie_genre_effect.details .sidebar }
##### Details
\
The dataset passed in the [train.sgr](#func.train_user_movie_genre_effect.args.train.sgr) argument is assumed to be the result returned by the [splitGenreRows](#func.splitGenreRows) helper function described above in the *Data Helper Functions /* [Data Processing Functions] section of *this Appendix*.

@@

::: {.noteblock data-latex=""}
*Regularization* is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the *Common Helper Functions /* [Model Tuning Utils] section of *this Appendix*.
::: {.noteblock data-latex=""}
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above the `train_UMGY_SmoothedDay_effect.RMSE.cv.degree0` function is passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument to the [tune.model_param](#func.tune.model_param) function described above in the section *Common Helper Functions /* [Model Tuning Utils] of *this Appendix*.
:::
:::

@@

::: {.noteblock data-latex=""}
This is an auxiliary function intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Model Tuning Utils] section of *this Appendix*.
:::
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above the `train_UMGY_SmoothedDay_effect.RMSE.cv.degree1` function is passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument to the [model.tune.param_range](#func.model.tune.param_range) function described above in the section *Common Helper Functions /* [Model Tuning Utils] of *this Appendix*.
:::
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above the `train_UMGY_SmoothedDay_effect.RMSE.cv.degree2` function is passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument to the [model.tune.param_range](#func.model.tune.param_range) function described above in the section *Common Helper Functions /* [Model Tuning Utils] of *this Appendix*.
:::
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above this function is passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument to the [model.tune.param_range](#func.model.tune.param_range) function described above in the section *Common Helper Functions /* [Model Tuning Utils] of *this Appendix*.

>>>>

::: {.noteblock data-latex=""}
In the sample code snippet above, the `mean_reg` function is called internally from the [train_user_movie_effect](#func.train_user_movie_effect) function described below in section [Models Training: Support Functions]/[UME Model: Utility Functions] of *this Appendix*.
:::
:::

@@

::: {.noteblock data-latex=""}
*Regularization* is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the [Common Helper Functions]/[Model Tuning Utils] section of *this Appendix*.
:::
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above this function is passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument to the [tune.model_param](#func.tune.model_param) function described above in the section [Common Helper Functions]/[Model Tuning Utils] of *this Appendix*.

@@

::: {.noteblock data-latex=""}
This function is an auxiliary function specifically designed to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the [Common Helper Functions]/[Model Tuning Utils] section of *this Appendix*.
:::
:::

@@

::: { #func.train_user_movie_genre_effect.details .sidebar }
##### Details
\
The dataset passed in the [train.sgr](#func.train_user_movie_genre_effect.args.train.sgr) argument is assumed to be the result returned by the [splitGenreRows](#func.splitGenreRows) helper function described above in the [Data Helper Functions]/[Data Processing Functions] section of *this Appendix*.

@@

::: {.noteblock data-latex=""}
*Regularization* is committed through the *penalized regression* by computing the *penalized mean* performed by the internally called [mean_reg](#func.mean_reg) function described above in the [Common Helper Functions]/[Model Tuning Utils] section of *this Appendix*.
::: {.noteblock data-latex=""}
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above the `train_UMGY_SmoothedDay_effect.RMSE.cv.degree0` function is passed in the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument to the [tune.model_param](#func.tune.model_param) function described above in the section [Common Helper Functions]/[Model Tuning Utils] of *this Appendix*.
:::
:::

@@

::: {.noteblock data-latex=""}
This is an auxiliary function intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the [Common Helper Functions]/[Model Tuning Utils] section of *this Appendix*.
:::
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above the `train_UMGY_SmoothedDay_effect.RMSE.cv.degree1` function is passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument to the [model.tune.param_range](#func.model.tune.param_range) function described above in the section [Common Helper Functions]/[Model Tuning Utils] of *this Appendix*.
:::
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above the `train_UMGY_SmoothedDay_effect.RMSE.cv.degree2` function is passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument to the [model.tune.param_range](#func.model.tune.param_range) function described above in the section [Common Helper Functions]/[Model Tuning Utils] of *this Appendix*.
:::
:::

@@

::: {.noteblock data-latex=""}
In the code snippet above this function is passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument to the [model.tune.param_range](#func.model.tune.param_range) function described above in the section [Common Helper Functions]/[Model Tuning Utils] of *this Appendix*.
